Compiling refinement types to dependent types

### 2020-07-07 tex/paper.tex
Proper recursion in the definition of \mu_\Gamma
Update the terms translation function

We start with defining $\mu_\Gamma$,
which merely translates the types of the bindings from the surface language into the core language:
\begin{equation}
\begin{aligned}
  & \mu_\Gamma(\emptyset)                                       && \triangleq \emptyset                                                     \\
  & \mu_\Gamma(\nonterm G, \gterm x : \nonterm{ts})             && \triangleq \nonterm{GC},
                                                                    \gterm x : \mu_\tau(\nonterm{ts})                                       \\
\end{aligned}
\end{equation}

$\mu_\tau$ is defined as follows:
\begin{equation}
\begin{aligned}
  & \mu_\tau( (x : \nonterm{ts}_1) \rightarrow \nonterm{ts}_2)  && \triangleq \Pi x : \mu_\tau(\nonterm{ts}_1). \mu_\tau(\nonterm{ts}_2)  \\
  & \mu_\tau( \{ v : \nonterm{ts} | \nonterm{r} \})             && \triangleq \{ v : \mu_\tau(\nonterm{ts})\ **\ \mu_\tau(\nonterm r) \}  \\
  & \mu_\tau( \nonterm r_1 \land \nonterm r_2 )                 && \triangleq ( \mu_\tau(\nonterm r_1) , \mu_\tau(\nonterm r_2))          \\
  & \mu_\tau( \nonterm{es} )                                    && \triangleq \mu_\varepsilon(\nonterm{es}) = \text{True}                 \\
%TODO add syntax/typing rules for True
  & \mu_\tau(B)                                                 && \triangleq B                                                           \\
\end{aligned}
\end{equation}
Or, in words:
\begin{itemize}
  \item (dependent) arrow types are translated to the corresponding $\Pi$-types,
  \item refined types are translated to the corresponding $\Sigma$-types,
  \item atomic refinements (which are $\text{Bool}$-typed terms) are translated to propositions stating that the corresponding term is equal to $\text{True}$,
  \item conjunctions of several (atomic) refinements are represented as tuples of the corresponding atomic translations.
\end{itemize}

>>>>

We start with defining $\mu_\Gamma$,
which merely translates the types of the bindings in the context from the surface language into the core language:
\begin{equation}
\begin{aligned}
  & \mu_\Gamma(\emptyset)                                       && \triangleq \emptyset                                                     \\
  & \mu_\Gamma(\nonterm G, \gterm x : \nonterm{ts})             && \triangleq \mu_\Gamma(\nonterm G), \gterm x : \mu_\tau(\nonterm{ts})     \\
\end{aligned}
\end{equation}

$\mu_\tau$ is defined as follows:
\begin{equation}
\begin{aligned}
  & \mu_\tau( (x : \nonterm{ts}_1) \rightarrow \nonterm{ts}_2)  && \triangleq \Pi x : \mu_\tau(\nonterm{ts}_1). \mu_\tau(\nonterm{ts}_2)        \\
  & \mu_\tau( \{ v : \nonterm{ts} | \nonterm{r} \})             && \triangleq \{ v : \mu_\tau(\nonterm{ts})\ **\ \mu_\tau(\nonterm r) \}        \\
  & \mu_\tau( \nonterm r_1 \land \nonterm r_2 )                 && \triangleq ( \mu_\tau(\nonterm r_1) , \mu_\tau(\nonterm r_2))                \\
  & \mu_\tau( \nonterm{es}_1 = \nonterm{es}_2 )                 && \triangleq \mu_\varepsilon(\nonterm{es}_1) = \mu_\varepsilon(\nonterm{es}_2) \\
%TODO add syntax/typing rules for True
  & \mu_\tau(B)                                                 && \triangleq B                                                                 \\
\end{aligned}
\end{equation}
Or, in words:
\begin{itemize}
  \item (dependent) arrow types are translated to the corresponding $\Pi$-types,
  \item refined types are translated to the corresponding $\Sigma$-types,
  \item atomic refinements, being propositions about surface language terms equality,
    are translated to propositions stating the equality of translated core language terms,
  \item conjunctions of several (atomic) refinements are represented as tuples of the corresponding atomic translations.
\end{itemize}
